HW-Lego-YanniSun

```{r include=FALSE}
library(tidyverse)
library(dsbox)
library(dplyr)
```

### Question 1: What are the three most common first names of purchasers?  
**Answer: In this sample, the first three common names of purchasers are "Jackson", "Jacob" and "Abraham Medlock"Joseph"**
```{r}
lego_sales %>%
    group_by(first_name) %>%
    summarise(n=n()) %>%
    arrange(desc(n)) 
```


### Question 2: What are the three most common themes of Lego sets purchased?  
**Answer: In this sample, the three most common themes of Lego sets purchased are "Star Wars", "Josie Paley"Nexo Knights" and "Abraham Medlock"Mixels"**
```{r}
lego_sales %>%
    group_by(theme) %>%
    summarise(n=sum(quantity)) %>%
    arrange(desc(n)) 
```

### Question 3: Among the most common theme of Lego sets purchased, what is the most common subtheme?  
**Answer: In this sample, among the most common theme of Lego sets purchased "Star Wars", the most common subtheme is "The Force Awakens".**
```{r}
lego_sales %>%
    filter(theme=="Star Wars") %>%
    group_by(subtheme) %>%
    summarise(n=sum(quantity)) %>%
    arrange(desc(n)) 
```

### Question 4: Create a new variable called age_group and group the ages into the following categories: “18 and under”, “19 - 25”, “26 - 35”, “36 - 50”, “51 and over”.
```{r}
age_group <- lego_sales %>%
  mutate(age_group = case_when(
                           age<=18 ~ "18 and under",
                           between(age,19,25) ~ "19 - 25",
                           between(age,26,35) ~ "26 - 35",
                           between(age,36,50) ~ "36 - 50",
                           age>=51 ~ "51 and over",
                           TRUE ~ as.character(age))) 
age_group
```

### Question 5: Which age group has purchased the highest number of Lego sets.  
**Answer: In this sample,age group 36-50 has purchased the highest number of Lego sets.**
```{r}
age_group %>%
  group_by(age_group) %>%
  summarise(number=sum(quantity)) %>%
  arrange(desc(number))
```


### Question 6: Which age group has spent the most money on Legos?  
**Answer: In this sample, age group 36-50 has spent the most money on Legos.**
```{r}
age_group %>%
  group_by(age_group) %>%
  summarise(money=sum(us_price*quantity)) %>%
  arrange(desc(money))
```

### Question 7: Which Lego theme has made the most money for Lego?  
**Answer: In this sample, theme "Star Wars" has made the most money for Lego.**
```{r}
lego_sales %>%
  group_by(theme) %>%
  summarise(money=sum(us_price*quantity)) %>%
  arrange(desc(money))
```


## Question 8: Which area code has spent the most money on Legos? In the US the area code is the first 3 digits of a phone number.  
**Answer: In this sample, area code 956 has spent the most money on Legos.**
```{r}
lego_sales %>%
  transmute(area_code=str_sub(phone_number,1,3), us_price,quantity) %>%
  group_by(area_code) %>%
  summarise(money=sum(us_price*quantity)) %>%
  arrange(desc(money))
```
 
### Question 9: Come up with a question you want to answer using these data, and write it down. Then, create a data visualization that answers the question, and explain how your visualization answers the question.  
**Answer: I am interest in how many orders that each age group made and what kind of price Legos that people ordered most. From below plot, we can find that for all age group, people would like to buy Legos with price lower than 10 dollars.**

```{r}
age_group %>%
  mutate(price_group = case_when(
                           us_price<=10 ~ "10 and under",
                           between(us_price,11,20) ~ "11 - 20",
                           between(us_price,21,30) ~ "21 - 30",
                           between(us_price,31,40) ~ "31 - 40",
                           between(us_price,41,50) ~ "41 - 50",
                           between(us_price,51,100) ~ "51 - 100",
                           us_price>=100 ~ "100 and over",
                           TRUE ~ as.character(us_price))) %>%
  ggplot(aes(x=age_group,fill=price_group)) +
   geom_bar() +
   theme(axis.text.x = element_text(angle=15, hjust=1))
```




